\documentclass[11pt, letterpaper, sans]{moderncv}
\moderncvstyle{classic}                            % style options are 'casual' (default), 'classic', 'oldstyle' and 'banking'
\moderncvcolor{blue}                                % color options 'blue' (default), 'orange', 'green', 'red', 'purple', 'grey' and 'black'

% character encoding
\usepackage[utf8]{inputenc}                       % if you are not using xelatex ou lualatex, replace -by the encoding you are using

% adjust the page margins
\usepackage[scale=0.8]{geometry}
%\setlength{\hintscolumnwidth}{3cm}                % if you want to change the width of the column with the dates
%\setlength{\makecvtitlenamewidth}{10cm\\}           % for the 'classic' style, if you want to force the width allocated to your name and avoid line breaks. be careful though, the length is normally calculated to avoid any overlap with your personal info; use this at your own typographical risks...

\usepackage{import}
\usepackage{footmisc}
\usepackage{multicol}
\usepackage{float}
\newcommand{\tabitem}{~~\llap{\textbullet}~~}

% personal data
\name{Juan Sebasti\'an}{Barbosa}
%\address{}{Bogot\'a, Colombia}{}% optional, remove / comment the line if not wanted; the "postcode city" and and "country" arguments can be omitted or provided empty
\phone[mobile]{+57 316 794 6510}                   % optional, remove / comment the line if not wanted
%\phone[fixed]{6135083}                    % optional, remove / comment the line if not wanted
%\phone[fax]{+3~(456)~789~012}                      % optional, remove / comment the line if not wanted
\email{jsbarbosacoy@hotmail.com}                               % optional, remove / comment the line if not wanted
\homepage{https://www.linkedin.com/in/jsbarbosacoy/}                         % optional, remove / comment the line if not wanted
%\extrainfo{Bogotá, Colombia}                 % optional, remove / comment the line if not wanted
%\photo[64pt][0.4pt]{picture}                       % optional, remove / comment the line if not wanted; '64pt' is the height the picture must be resized to, 0.4pt is the thickness of the frame around it (put it to 0pt for no frame) and 'picture' is the name of the picture file
%\quote{Some quote}                                 % optional, remove / comment the line if not wanted

% to show numerical labels in the bibliography (default is to show no labels); only useful if you make citations in your resume
%\makeatletter
%\renewcommand*{\bibliographyitemlabel}{\@biblabel{\arabic{enumiv}}}
%\makeatother
%\renewcommand*{\bibliographyitemlabel}{[\arabic{enumiv}]}% CONSIDER REPLACING THE ABOVE BY THIS

%\definecolor{color3}{rgb}{0.50,0.33,0.80}% purple
\definecolor{color3}{rgb}{0.93,0.56,0.30}% orange
\definecolor{color3}{rgb}{0.63,0.26,0.00}% orange

% bibliography with mutiple entries
%\usepackage{multibib}
%\newcites{book,misc}{{Books},{Others}}
%----------------------------------------------------------------------------------
%            content
%----------------------------------------------------------------------------------
\begin{document}
%-----       resume       ---------------------------------------------------------
\maketitle
Data Team Lead | Data Engineer | Data Architect | Credit Risk Specialist
\vspace{0.5cm}
\\
\small{
Physicist and chemist with experience leveraging data to improve business results. Skilled in data strategy, infrastructure development, and cloud computing. Effective at collaborating across teams and guiding projects with data. Proficient in AWS services, data pipelines, and machine learning, with a focus on performance optimization and cost reduction.
}

\section{Experience}
    \cventry{October 2022--June 2024}{Head of Data}{Foodology}{}{}
    {
        Creator and operator of virtual restaurant brands. \url{https://www.foodology.com.co/}
        \vspace{3pt}
        \begin{itemize}
            \item Led Foodology's data strategy, contributing to doubling the efficiency of the operations and supply team by using data assets.
            \item Increased company-wide data usage by 20x by deploying \href{https://superset.apache.org/}{\color{color3} Apache Superset}, giving to more than 200 employees access to data.
            \item Managed and scaled a team of 4 data analysts, 3 data engineers, and 1 data scientist, increasing project delivery speed by 2x.
            \item Implemented \href{https://airflow.apache.org/}{\color{color3}{Apache Airflow}} to automate over 100 ETL processes, reducing downtime and raising job success rates to 99 \%.
            \item Cut cloud infrastructure costs by 30 \%, doubling data capacity by optimizing AWS solutions and redesigning architecture.
            \item Led the deployment of a machine learning model to assess the launching of influencer brands, potentially increasing sales up to 20 \%.
            \item Earned Rocket recognition twice, achieving 9.85/10 Leadership Feedback and raising team eNPS from 50 to 88.
        \end{itemize}
    }

    \cventry{July 2019--October 2022}{Data partner}{Zinobe - Tangelo Latam}{}{}
    {
        Technology company specializing in alternative credit. \url{https://www.tangelolatam.com/}
        \vspace{3pt}
        \begin{itemize}
            \item Created an Machine Learning model for automatic loan approvals, \href{https://forbes.co/2020/05/13/emprendedores/zinobe-obtiene-us30-millones-en-financiacion-para-otorgar-mas-creditos-digitales}{\color{color1} increasing loan coverage by 4,000 low-income Colombians and disbursing 6,000 loans during the pandemic.}
            \item Developed a \href{https://tekiosmag.com/2022/03/31/fintech-tangelo-anuncia-alianza-con-el-unicornio-mexicano-clip-y-dell-leasing/}{\color{color1} Merchant Cash Advance scoring system for Mexico terminal operators}, resulting in over 10,000 disbursements.
            \item Built a decision support system that sped up SME credit evaluations to a single day.
            \item Led the development of a \href{https://psychometrics.zinobe.com/v1/}{\color{color1}psychometrics scoring system}, increasing approval rates by 10 \% through behavioral loan assessment tests.
            \item Built {\color{color3} Django}-based system for \href{https://contxto.com/es/fondeo/fintech-zinobe-levanta-inversion-monachil-capital-partners/}{\color{color1} portfolio allocation handling 30 million USD.}
        \end{itemize}
    }

    \cventry{January 2017--January 2021}{Software Developer}{Tausand Electronics}{}{}
    {
        Scientific instrumentation development company. \url{https://www.tausand.com/}
        \vspace{3pt}
        \begin{itemize}
            \item Designed and developed \href{https://www.tausand.com/downloads/}{\color{color1} \texttt{Abacus}} software and interface libraries in {\color{color3} Python} for experiment customization, leading to \href{https://pypistats.org/packages/pyabacus}{\color{color1} about 100 monthly downloads.}
        \end{itemize}
    }

    \cventry{January 2018--June 2019}{Research assistant}{Universidad de los Andes, Centro de Microscopía}{}{}
    {
        \url{https://investigaciones.uniandes.edu.co/es/microscopia/}
        \vspace{3pt}
        \begin{itemize}
            \item Automated image analysis techniques, cutting manual analysis time by 20 \%.
            \item Built \href{https://github.com/jsbarbosa/microbill}{\color{color1} Microbill} (CRM software), boosting service tracking and invoicing efficiency by 100 \%.
            \item Created \href{https://github.com/jsbarbosa/SPM}{\color{color1} Igor Extractor} an Atomic Force Microscope data extraction software, cutting data processing time by 50 \%.
        \end{itemize}
    }

    \cventry{August 2016--December 2017}{Teaching assistant of Computational Methods}{Universidad de los Andes, Departamento de Física}{}{}
    {
        \vspace{3pt}
        \begin{itemize}
            \item Developed educational libraries for gravitational and wave simulations (\href{https://jsbarbosa.github.io/astrohut/}{\color{color1} AstroHut}, \href{https://jsbarbosa.github.io/rippleTank/}{\color{color1} rippleTank}), with \href{https://pypistats.org/packages/astrohut}{\color{color1} 100+ monthly downloads.}
            \item Published \href{https://github.com/ComputoCienciasUniandes/Demonstrations}{\color{color1} a set of computer simulations} to increase students interest in programming abilities.
        \end{itemize} 
    }

\section{Education}
\subsection{Majors}
\vspace{5pt}
    \cventry{2013--2019}{Physicist}{Universidad de los Andes}{Colombia}{GPA: 4.01/5.00}{}
    \cventry{2014--2019}{Chemist}{Universidad de los Andes}{Colombia}{GPA: 4.01/5.00}{}
\vspace{5pt}
\subsection{Certifications}
	\cventry{2022--2022}{Nanodegree: Data Architect}{Udacity}{}{}{}
	\cventry{2021--2021}{Nanodegree: Data Engineering}{Udacity}{}{}{}
    \cventry{2020--2020}{Data Science For All}{Correlation One - MinTIC}{Colombia}{375 hours}{}
    \cventry{2020--2020}{Scrum Foundation Professional Certificate}{CertiProf}{}{}{}

\section{Hard \& Soft skills}
{
    \center
    \begin{tabular}{p{0.5\linewidth}p{0.05\linewidth}p{0.45\linewidth}}
        %\color{color1} Hard Skills & & \color{color1} Soft Skills \\
        \begin{itemize}
            \item Programming ({\color{color3} Python}, {\color{color3} C}, {\color{color3} Java}, {\color{color3} R})
            \item Cloud Computing ({\color{color3} AWS}, {\color{color3} GCP})
            \item Database Management ({\color{color3} SQL}, {\color{color3} MongoDB}, {\color{color3} Cassandra})
            \item ETL Pipeline Development ({\color{color3} Airflow})
            \item Data Analysis and Modeling
            \item Data Visualization ({\color{color3} Superset}, {\color{color3} Tableau}, {\color{color3} Power BI})
            \item Machine Learning and AI ({\color{color3} Scikit-learn}, {\color{color3} Tensorflow})
        \end{itemize}
        &
        & 
        \begin{itemize}
            \item Leadership and Team Management
            \item Problem-solving and Critical Thinking
            \item Communication and Collaboration
            \item Project Management
            \item Adaptability and Continuous Learning
        \end{itemize}
    \end{tabular}
}

\section{Achievements \& Projects}
{
    \center
    \begin{tabular}{p{0.5\linewidth}p{0.05\linewidth}p{0.45\linewidth}}
        \begin{itemize}
            \item Automated 100+ ETL processes with {\color{color3} Airflow}, reducing downtime and boosting job success rate to 99 \%.
            \item Reduced cloud infrastructure costs by 30 \% while doubling data capacity.
            \item Built a statistical model that facilitated 6,000 loan approvals, benefiting 4,000 low-income Colombians.
            \item Led a cross-functional data team to achieve an eNPS increase from 50 to 88 within two years.
        \end{itemize}
        &
        & 
        \begin{itemize}
            \item \textbf{Abacus Software:} Interface libraries with 100 monthly downloads.
            \item \textbf{Microbill CRM:} CRM streamlining invoicing and service tracking.
            \item \textbf{Merchant Scoring}: System responsible for over 10,000 disbursements.
            \item \textbf{Portfolio Allocation Tool:} Automate portfolio allocation for 30 million USD.
        \end{itemize}
    \end{tabular}
}

\section{Languages}
{
    \center
    \begin{tabular}{p{0.5\linewidth}p{0.05\linewidth}p{0.45\linewidth}}
        \begin{itemize}
	       \item \textbf{English:} Fluent (C1). IELTS certificate (7.0/9.0)
        \end{itemize}
        &
        & 
        \begin{itemize}  
	       \item \textbf{Spanish:} Native speaker
        \end{itemize}
    \end{tabular}
}

\section{Extracurricular activities}
    \cventry{May 2019}{Participant}{Machine Learning for Quantum Matter and Technology}{Décima Escuela de F\'isica Matem\'atica}{}{}
    
    \cventry{April 2019}{Collaborator}{Sympy}{}{}{}
    %\cventry{October 2018}{Exhibitor}{Expociencia, Uniandes en Corferias}{}{}{}
    \cventry{April 2017}{Organizer}{Python Bootcamp Uniandes, Universidad de los Andes}{}{}{}

\end{document}

